Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-10-01 submission/empirical2_NatComfmt.tex
pass to address most of the presubmission comments for nat comm

% Here are two macros for comments.
\newcommand {\nred}[1]{{\color{red}\sf{[#1]}}}
\newcommand {\ngreen}[1]{{\color{green}\sf{[#1]}}}
\newcommand {\ncyan}[1]{{\color{cyan}\sf{[#1]}}}
\newcommand {\michael}[1]{{\color{red}\sf{[michael: #1]}}}
\newcommand {\charles}[1]{{\color{blue}\sf{[charles: #1]}}}
\newcommand {\serena}[1]{{\color{orange}\sf{[charles: #1]}}}

@@

\author{%
Charles H. Martin\thanks{Calculation Consulting, 8 Locksley Ave, 6B, San Francisco, CA 94122, \texttt{charles@CalculationConsulting.com}.} 
\and 
Tongsu (Serena) Peng\thanks{Calculation Consulting, 8 Locksley Ave, 6B, San Francisco, CA 94122, \texttt{serenapeng7@gmail.com}.}
\and
Michael W. Mahoney\thanks{ICSI and Department of Statistics, University of California at Berkeley, Berkeley, CA 94720, \texttt{mmahoney@stat.berkeley.edu}.}
}

@@

\input{NatCom_introduction}
\input{NatCom_methods}

\section{Results}
We study in detail three well-known CV architectures (the VGG, ResNet, and DenseNet series of models).
Then, we look in detail at several variations of a popular NLP architecture (the OpenAI GPT and GPT2 models).
Finally, we present results from a broader analysis of hundreds of pretrained DNN~models.

\input{NatCom_cv_models}
\input{NatCom_nlp_models}
\input{NatCom_all_models}

@@

>>>>

% Here are two macros for comments.
\newcommand {\nred}[1]{{\color{red}\sf{[#1]}}}
\newcommand {\ngreen}[1]{{\color{green}\sf{[#1]}}}
\newcommand {\ncyan}[1]{{\color{cyan}\sf{[#1]}}}

%% MWM: Do the following to remove the comments from the pdf.
%\newcommand {\michael}[1]{{ }}
\newcommand {\michael}[1]{{\color{red}\sf{[michael: #1]}}}

\newcommand {\charles}[1]{{\color{blue}\sf{[charles: #1]}}}
\newcommand {\serena}[1]{{\color{orange}\sf{[charles: #1]}}}

@@

\author{%
Charles H. Martin\thanks{Calculation Consulting, 8 Locksley Ave, 6B, San Francisco, CA 94122, \texttt{charles@CalculationConsulting.com}.} 
\and 
Tongsu (Serena) Peng\thanks{Calculation Consulting, 8 Locksley Ave, 6B, San Francisco, CA 94122, \texttt{serenapeng7@gmail.com}.}
\and
Michael W. Mahoney\thanks{ICSI and Department of Statistics, University of California at Berkeley, Berkeley, CA 94720, \texttt{mmahoney@stat.berkeley.edu}.}
\thanks{Corresponding author.}
}

@@

\input{NatCom_introduction}

\section{Results}
After describing our overall approach, we study in detail three well-known CV architectures (the VGG, ResNet, and DenseNet series of models).
Then, we look in detail at several variations of a popular NLP architecture (the OpenAI GPT and GPT2 models), and we present results from a broader analysis of hundreds of pretrained DNN~models.

\input{NatCom_overall_approach}
\input{NatCom_cv_models}
\input{NatCom_nlp_models}
\input{NatCom_all_models}

@@

\input{NatCom_methods}
